Nodal Discontinuous Galerkin Method for the Euler Equations in GR

### 2018-10-23 Documents/Euler/dgEulerGR.tex
Modified source-term time-step derivation and added proof of validity of using nodal points for higher-order methods

Substituting \eqref{Eq:LLF} with \eqref{Eq:EigVals} into \eqref{Eq:1stOrderDG}:
\begin{align}
    \ol{\bU}^{n+1}_{i}&=\ol{\bU}^{n}_{i}-\f{\eta_{i}}{2}\left[\bF\left(\ol{\bU}^{n}_{i}\right)+\bF\left(\ol{\bU}^{n}_{i+1}\right)-\alpha_{\iph}\left(\ol{\bU}^{n}_{i+1}-\ol{\bU}^{n}_{i}\right)\right.\nonumber\\
    &\left.\hspace{7em}-\bF\left(\ol{\bU}^{n}_{i}\right)-\bF\left(\ol{\bU}^{n}_{i-1}\right)+\alpha_{\imh}\left(\ol{\bU}^{n}_{i}-\ol{\bU}^{n}_{i-1}\right)\right]\nonumber\\
    &=\left[1-\f{\eta_{i}}{2}\left(\alpha_{\iph}+\alpha_{\imh}\right)\right]\ol{\bU}^{n}_{i}+\f{\eta_{i}}{2}\,\alpha_{\iph}\left[\ol{\bU}^{n}_{i+1}-\f{1}{\alpha_{\iph}}\bF\left(\ol{\bU}^{n}_{i+1}\right)\right]\nonumber\\
    &\hspace{15em}+\f{\eta_{i}}{2}\,\alpha_{\imh}\left[\ol{\bU}^{n}_{i-1}+\f{1}{\alpha_{\imh}}\bF\left(\ol{\bU}^{n}_{i-1}\right)\right]\nonumber\\
    &=\left[1-\f{\eta_{i}}{2}\left(\alpha_{\iph}+\alpha_{\imh}\right)\right]\ol{\bU}^{n}_{i}+\f{\eta_{i}}{2}\,\alpha_{\iph}\,\bH^{-}\left(\ol{\bU}^{n}_{i+1},\alpha_{\iph}\right)+\f{\eta_{i}}{2}\,\alpha_{\iph}\,\bH^{+}\left(\ol{\bU}^{n}_{i-1},\alpha_{\imh}\right),\label{Eq:ConvComb}
\end{align}
where
\begin{equation}\label{Eq:Hpm}
    \bH^{\pm}\left(\ol{\bU},\alpha\right)\equiv\ol{\bU}\pm\f{1}{\alpha}\,\bF\left(\ol{\bU}\right).
\end{equation}

The proof that $\bH^{\pm}\in\cG$ is given in \citet{Qin2016}. Therefore, we see that with a restriction on $\alpha_{i\pm\f{1}{2}}$ that \eqref{Eq:ConvComb} is a convex combination. The restriction is (recalling that $\eta_{i}=\Delta t_{i}/\Delta x_{i}$):
\begin{equation}
    1-\f{\eta_{i}}{2}\left(\alpha_{\iph}+\alpha_{\imh}\right)>0\implies\f{\eta_{i}}{2}\left(\alpha_{\iph}+\alpha_{\imh}\right)<1\implies \Delta t_{i}<\f{2\,\Delta x_{i}}{\alpha_{\iph}+\alpha_{\imh}}\leq\f{\Delta x_{i}}{\text{max}\left(\alpha_{i\pm\f{1}{2}}\right)}.
\end{equation}

@@

\subsection{Curvilinear Coordinates}
NOTE: We assume a conformally-flat, time-independent spatial three-metric.

\subsubsection{Set of Admissible States}
We again consider a one-dimensional system of conservation laws, but this time with a curvilinear metric:
\begin{equation}
    \pd{\left(\sqrtgm\,\bU\right)}{t}+\pd{\left(\sqrtgm\,\bF\right)}{1}=\sqrtgm\,\bQ,
\end{equation}
where $\bU$ is given by:
\begin{equation}
    \bU\longrightarrow\begin{pmatrix} D\\ S_{1}\\ \tau\end{pmatrix}=\begin{pmatrix} \rho\,W\\ \rho\,h\,W^{2}\,v_{1}\\ \rho\,W\left(h\,W-1\right)-p\end{pmatrix}=\begin{pmatrix} \rho\,W\\ \rho\,h\,W^{2}\,\gamma_{1j}\,v^{j}\\ \rho\,W\left(h\,W-1\right)-p\end{pmatrix},
\end{equation}
$\bF\left(\bU\right)$ are the fluxes of those conserved quantities:
\begin{equation}
    \bF\left(\bU\right)\longrightarrow\begin{pmatrix}D\,v^{1}\\ S^{1}\,v_{1}+p\,\delta^{1}_{~1}\\ S^{1}-D\,v^{1}\end{pmatrix}=\begin{pmatrix}\rho\,W\,v^{1}\\ \rho\,h\,W^{2}\,v^{1}\,v_{1}+p\\\rho\,h\,W^{2}\,v^{1}-D\,v^{1}\end{pmatrix}=\begin{pmatrix}\rho\,W\,v^{1}\\ \rho\,h\,W^{2}\,\gamma_{1j}\,v^{1}\,v^{j}+p\\\rho\,h\,W^{2}\,v^{1}-D\,v^{1}\end{pmatrix},
\end{equation}
and $\bQ$ is a source term:
\begin{align}
    \bQ\longrightarrow\begin{pmatrix}0\\\f{1}{2}\,P^{kj}\,\pd{\gamma_{kj}}{1}\\0\end{pmatrix}&=\begin{pmatrix}0\\ \f{1}{2}\left[P^{11}\,\pd{\gamma_{11}}{1}+P^{22}\,\pd{\gamma_{22}}{1}+P^{33}\,\pd{\gamma_{33}}{1}\right] \\0\end{pmatrix}\\
    &=\begin{pmatrix}0\\ P^{11}\,h_{1}\,\pd{\,h_{1}}{1}+P^{22}\,h_{2}\,\pd{\,h_{2}}{1}+P^{33}\,h_{3}\,\pd{\,h_{3}}{1} \\0\end{pmatrix},
\end{align}
where we have used the fact that $\gamma_{jj}=\left(h_{j}\right)^{2}$. The $P^{kj}$ are components of the pressure tensor:
\begin{equation}
    P^{kj}=S^{k}\,v^{j}+p\,\gamma^{kj}=\gamma^{kj}\left[S_{a}\,v^{a}+p\right].
\end{equation}

@@

Before continuing, we show that the introduction of the metric doesn't affect the translation between $\cG_{p}$ and $\cG$...\sd{Need to do this}

@@

So, we get:
\begin{align}
    \ol{\bU}^{n+1}_{i}&=\ve\left\{\ol{\bU}^{n}_{i}-\f{\Delta t_{i}}{\ve\,\Delta V_{i}}\left[\sqrtgm_{\iph}\,\hat{\bF}^{n}_{\iph}-\sqrtgm_{\imh}\,\hat{\bF}^{n}_{\imh}\right]\right\}+\left(1-\ve\right)\ol{\bU}^{n}_{i}+\Delta t_{i}\,\ol{\bQ}^{n}_{i}\\
    &=\ve\left\{\ol{\bU}^{n}_{i}-\eta_{i}\left[\sqrtgm_{\iph}\,\hat{\bF}\left(\ol{\bU}^{n}_{i+1},\ol{\bU}^{n}_{i}\right)-\sqrtgm_{\imh}\,\hat{\bF}\left(\ol{\bU}^{n}_{i},\ol{\bU}^{n}_{i-1}\right)\right]\right\}+\left(1-\ve\right)\ol{\bU}^{n}_{i}+\Delta t_{i}\,\ol{\bQ}^{n}_{i}\\
    &=\ve\,\bH_{1}+\left(1-\ve\right)\bH_{2},
\end{align}
where
\begin{equation}
    \bH_{1}\equiv \ol{\bU}^{n}_{i}-\eta_{i}\left[\sqrtgm_{\iph}\,\hat{\bF}\left(\ol{\bU}^{n}_{i+1},\ol{\bU}^{n}_{i}\right)-\sqrtgm_{\imh}\,\hat{\bF}\left(\ol{\bU}^{n}_{i},\ol{\bU}^{n}_{i-1}\right)\right],
\end{equation}
\begin{equation}
    \bH_{2}\equiv\ol{\bU}^{n}_{i}+\f{\Delta t_{i}}{1-\ve}\,\ol{\bQ}^{n}_{i},
\end{equation}
and
\begin{equation}
    \eta_{i}\equiv\f{\Delta t_{i}}{\ve\,\Delta V_{i}}.
\end{equation}

We proceed by focusing on each term individually, starting with the numerical flux term, $\bH_{1}$.

\subsubsection{Numerical flux term}
We have to show that $\bH_{1}\in\cG$. We again we use the Local-Lax-Friedrichs flux, \eqref{Eq:LLF}, yielding for $\bH_{1}$:
\begin{align}
    \ol{\bU}^{n}_{i}-\f{\eta_{i}}{2}\Big\{&\sqrtgm_{\iph}\left[\bF\left(\ol{\bU}^{n}_{i+1}\right)+\bF\left(\ol{\bU}^{n}_{i}\right)-\alpha_{\iph}\left(\ol{\bU}^{n}_{i+1}-\ol{\bU}^{n}_{i}\right)\right]\\
    &-\sqrtgm_{\imh}\left[\bF\left(\ol{\bU}^{n}_{i}\right)+\bF\left(\ol{\bU}^{n}_{i-1}\right)-\alpha_{\imh}\left(\ol{\bU}^{n}_{i}-\ol{\bU}^{n}_{i-1}\right)\right]\Big\}\\
    &\hspace{-10em}=\left(1-\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}-\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\right)\ol{\bU}^{n}_{i}\\
    &\hspace{-8em}-\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\bF\left(\ol{\bU}^{n}_{i}\right)+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\bF\left(\ol{\bU}^{n}_{i}\right)\\
    &\hspace{-8em}+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\left[\ol{\bU}^{n}_{i-1}+\f{1}{\alpha_{\imh}}\bF\left(\ol{\bU}^{n}_{i-1}\right)\right]+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\left[\ol{\bU}^{n}_{i+1}-\f{1}{\alpha_{\iph}}\bF\left(\ol{\bU}^{n}_{i+1}\right)\right].
\end{align}
Now we add and subtract $\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\,\ol{\bU}^{n}_{i}$ and $\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\,\ol{\bU}^{n}_{i}$, yielding:
\begin{align}
    &\left(1-\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}-\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\right)\ol{\bU}^{n}_{i}\\
    &+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\left[\ol{\bU}^{n}_{i}-\f{1}{\alpha_{\iph}}\bF\left(\ol{\bU}^{n}_{i}\right)\right]+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\left[\ol{\bU}^{n}_{i}+\f{1}{\alpha_{\imh}}\bF\left(\ol{\bU}^{n}_{i}\right)\right]\\
    &+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\left[\ol{\bU}^{n}_{i-1}+\f{1}{\alpha_{\imh}}\bF\left(\ol{\bU}^{n}_{i-1}\right)\right]+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\left[\ol{\bU}^{n}_{i+1}-\f{1}{\alpha_{\iph}}\bF\left(\ol{\bU}^{n}_{i+1}\right)\right].
\end{align}
All of the terms in square brackets are similar to the $\bH$ quantities in \citet{Qin2016}, and are therefore in $\cG$. It can easily be seen that the sum of the coefficients is unity. The final condition is that the coefficient of $\ol{\bU}^{n}_{i}>0$, or (recalling that $\eta_{i}=\Delta t_{i}/\left(\ve\,\Delta V_{i}\right)$):
\begin{align}
    1&-\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}-\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}>0\implies\eta_{i}\left(\sqrtgm_{\iph}\,\alpha_{\iph}+\sqrtgm_{\imh}\,\alpha_{\imh}\right)<1\\
    &\implies\Delta t_{i}<\f{\ve\,\Delta V_{i}}{\sqrtgm_{\iph}\,\alpha_{\iph}+\sqrtgm_{\imh}\,\alpha_{\imh}}\leq\f{\ve\,\Delta V_{i}}{2\,\text{max}\left(\sqrtgm_{i\pm\f{1}{2}}\,\alpha_{i\pm\f{1}{2}}\right)}.
\end{align}
Again we want a time-step that is the same for all elements at a given time, so:
\begin{equation}
    \Delta t<\text{min}_{i}\left(\f{\ve\,\Delta V_{i}}{2\,\text{max}\left(\sqrtgm_{i\pm\f{1}{2}}\,\alpha_{i\pm\f{1}{2}}\right)}\right).
\end{equation}

@@

\subsubsection{Source term}
For this section we drop the subscript $i$ and the superscript $n$. We have to show that $\bH_{2}\in\cG$, where
\begin{equation}
    \bH_{2}=\begin{pmatrix}\ol{D}\\ \ol{S}_{1}+\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\pd{\gamma_{kk}}{1}} \\ \ol{\tau}\end{pmatrix},\hspace{1em}\left(H_{2}\right)_{1}>0,\hspace{1em}\left(H_{2}\right)_{3}+\left(H_{2}\right)_{1}>\sqrt{\left(H_{2}\right)_{1}\left(H_{2}\right)_{1}+\left(H_{2}\right)_{2}\left(H_{2}\right)^{2}}.
\end{equation}

>>>>

Substituting \eqref{Eq:LLF} with \eqref{Eq:EigVals} into \eqref{Eq:1stOrderDG}:
\begin{align}
    \ol{\bU}^{n+1}_{i}&=\ol{\bU}^{n}_{i}-\f{\eta_{i}}{2}\left[\bF\left(\ol{\bU}^{n}_{i}\right)+\bF\left(\ol{\bU}^{n}_{i+1}\right)-\alpha_{\iph}\left(\ol{\bU}^{n}_{i+1}-\ol{\bU}^{n}_{i}\right)\right.\nonumber\\
    &\left.\hspace{7em}-\bF\left(\ol{\bU}^{n}_{i}\right)-\bF\left(\ol{\bU}^{n}_{i-1}\right)+\alpha_{\imh}\left(\ol{\bU}^{n}_{i}-\ol{\bU}^{n}_{i-1}\right)\right]\nonumber\\
    &=\left[1-\f{\eta_{i}}{2}\left(\alpha_{\iph}+\alpha_{\imh}\right)\right]\ol{\bU}^{n}_{i}+\f{\eta_{i}}{2}\,\alpha_{\iph}\left[\ol{\bU}^{n}_{i+1}-\f{1}{\alpha_{\iph}}\bF\left(\ol{\bU}^{n}_{i+1}\right)\right]\nonumber\\
    &\hspace{15em}+\f{\eta_{i}}{2}\,\alpha_{\imh}\left[\ol{\bU}^{n}_{i-1}+\f{1}{\alpha_{\imh}}\bF\left(\ol{\bU}^{n}_{i-1}\right)\right]\nonumber\\
    &=\left[1-\f{\eta_{i}}{2}\left(\alpha_{\iph}+\alpha_{\imh}\right)\right]\ol{\bU}^{n}_{i}+\f{\eta_{i}}{2}\,\alpha_{\iph}\,\ol{\bH}^{-}\left(\ol{\bU}^{n}_{i+1},\alpha_{\iph}\right)+\f{\eta_{i}}{2}\,\alpha_{\iph}\,\ol{\bH}^{+}\left(\ol{\bU}^{n}_{i-1},\alpha_{\imh}\right),\label{Eq:ConvComb}
\end{align}
where
\begin{equation}\label{Eq:Hpm}
    \ol{\bH}^{\pm}\left(\ol{\bU},\alpha\right)\equiv\ol{\bU}\pm\f{1}{\alpha}\,\bF\left(\ol{\bU}\right).
\end{equation}

The proof that $\ol{\bH}^{\pm}\in\cG$ is given in \citet{Qin2016}. Therefore, we see that with a restriction on $\alpha_{i\pm\f{1}{2}}$ that \eqref{Eq:ConvComb} is a convex combination. The restriction is (recalling that $\eta_{i}=\Delta t_{i}/\Delta x_{i}$):
\begin{equation}
    1-\f{\eta_{i}}{2}\left(\alpha_{\iph}+\alpha_{\imh}\right)>0\implies\f{\eta_{i}}{2}\left(\alpha_{\iph}+\alpha_{\imh}\right)<1\implies \Delta t_{i}<\f{2\,\Delta x_{i}}{\alpha_{\iph}+\alpha_{\imh}}\leq\f{\Delta x_{i}}{\text{max}\left(\alpha_{i\pm\f{1}{2}}\right)}.
\end{equation}

@@

\subsection{Curvilinear Coordinates}
NOTE: We assume a conformally-flat, time-independent spatial three-metric:
\begin{equation}
    \gamma_{ij}\left(x^{k},t\right)\longrightarrow\psi^{4}\left(x^{k}\right)\,\ol{\gamma_{ii}}\left(x^{k}\right),
\end{equation}
where $\psi\left(x^{k}\right)$ is the conformal factor and $\ol{\gamma}_{ii}$ is the flat-space metric.

\subsubsection{Set of Admissible States}
We again consider a one-dimensional system of conservation laws, but this time with a curvilinear metric:
\begin{equation}
    \pd{\left(\sqrtgm\,\bU\right)}{t}+\pd{\left(\sqrtgm\,\bF\right)}{1}=\sqrtgm\,\bQ,
\end{equation}
where $\bU$ is given by:
\begin{equation}
    \bU\longrightarrow\begin{pmatrix} D\\ S_{1}\\ \tau\end{pmatrix}=\begin{pmatrix} \rho\,W\\ \rho\,h\,W^{2}\,v_{1}\\ \rho\,W\left(h\,W-1\right)-p\end{pmatrix}=\begin{pmatrix} \rho\,W\\ \rho\,h\,W^{2}\,\gamma_{1j}\,v^{j}\\ \rho\,W\left(h\,W-1\right)-p\end{pmatrix},
\end{equation}
$\bF\left(\bU\right)$ are the fluxes of those conserved quantities:
\begin{equation}
    \bF\left(\bU\right)\longrightarrow\begin{pmatrix}D\,v^{1}\\ S^{1}\,v_{1}+p\,\delta^{1}_{~1}\\ S^{1}-D\,v^{1}\end{pmatrix}=\begin{pmatrix}\rho\,W\,v^{1}\\ \rho\,h\,W^{2}\,v^{1}\,v_{1}+p\\\rho\,h\,W^{2}\,v^{1}-D\,v^{1}\end{pmatrix}=\begin{pmatrix}\rho\,W\,v^{1}\\ \rho\,h\,W^{2}\,\gamma_{1j}\,v^{1}\,v^{j}+p\\\rho\,h\,W^{2}\,v^{1}-D\,v^{1}\end{pmatrix},
\end{equation}
and $\bQ$ is a source term:
\begin{align}
    \bQ\longrightarrow\begin{pmatrix}0\\\f{1}{2}\,P^{kj}\,\pd{\gamma_{kj}}{1}\\0\end{pmatrix}&=\begin{pmatrix}0\\ \f{1}{2}\left[P^{11}\,\pd{\gamma_{11}}{1}+P^{22}\,\pd{\gamma_{22}}{1}+P^{33}\,\pd{\gamma_{33}}{1}\right] \\0\end{pmatrix}\\
    &=\begin{pmatrix}0\\ P^{11}\,h_{1}\,\pd{\,h_{1}}{1}+P^{22}\,h_{2}\,\pd{\,h_{2}}{1}+P^{33}\,h_{3}\,\pd{\,h_{3}}{1} \\0\end{pmatrix},
\end{align}
where we have used the fact that $\gamma_{jj}=\left(h_{j}\right)^{2}$. The $P^{kj}$ are components of the pressure tensor:
\begin{equation}
    P^{kj}=S^{k}\,v^{j}+p\,\gamma^{kj}=\gamma^{k\ell}\,S_{\ell}\,v^{j}+p\,\gamma^{kj}=\gamma^{k\ell}\,S_{\ell}\,v^{j}+p\,\gamma^{k\ell}\,\delta^{j}_{~\ell}=\gamma^{k\ell}\left(S_{\ell}\,v^{j}+p\,\delta^{j}_{~\ell}\right).
\end{equation}
Since the spatial three-metric is diagonal we must have that $\ell=k$. We can therefore simplify further:
\begin{equation}
    P^{kj}=\gamma^{kk}\left(S_{k}\,v^{j}+p\,\delta^{j}_{~k}\right)=\f{1}{\gamma_{kk}}\,\left(S_{k}\,v^{j}+p\,\delta^{j}_{~k}\right)=\f{1}{\left(h_{k}\right)^{2}}\,\left(S_{k}\,v^{j}+p\,\delta^{j}_{~k}\right)
\end{equation}
For the pressure-tensor sum, we then have:
\begin{equation}\label{Eq:PressureTensorSum}
    P^{kj}\,\p_{1}\,\gamma_{kj}=P^{kk}\,\p_{1}\,\gamma_{kk}=P^{kk}\,\p_{1}\left(h_{k}\right)^{2}=2\,P^{kk}\,h_{k}\,\p_{1}\,h_{k}=\f{2}{h_{k}}\left(S_{k}\,v^{k}+p\right)\,\p_{1}\,h_{k}.
\end{equation}

@@

Before continuing, we show that the introduction of the metric doesn't affect the translation between $\cG_{p}$ and $\cG$...\sd{I've shown this, just need to TeX it up}

@@

So, we get:
\begin{align}
    \ol{\bU}^{n+1}_{i}&=\ve\left\{\ol{\bU}^{n}_{i}-\f{\Delta t_{i}}{\ve\,\Delta V_{i}}\left[\sqrtgm_{\iph}\,\hat{\bF}^{n}_{\iph}-\sqrtgm_{\imh}\,\hat{\bF}^{n}_{\imh}\right]\right\}+\left(1-\ve\right)\ol{\bU}^{n}_{i}+\Delta t_{i}\,\ol{\bQ}^{n}_{i}\\
    &=\ve\left\{\ol{\bU}^{n}_{i}-\eta_{i}\left[\sqrtgm_{\iph}\,\hat{\bF}\left(\ol{\bU}^{n}_{i+1},\ol{\bU}^{n}_{i}\right)-\sqrtgm_{\imh}\,\hat{\bF}\left(\ol{\bU}^{n}_{i},\ol{\bU}^{n}_{i-1}\right)\right]\right\}+\left(1-\ve\right)\ol{\bU}^{n}_{i}+\Delta t_{i}\,\ol{\bQ}^{n}_{i}\\
    &=\ve\,\ol{\bH}_{1}+\left(1-\ve\right)\ol{\bH}_{2},
\end{align}
where
\begin{equation}
    \ol{\bH}_{1}\equiv \ol{\bU}^{n}_{i}-\eta_{i}\left[\sqrtgm_{\iph}\,\hat{\bF}\left(\ol{\bU}^{n}_{i+1},\ol{\bU}^{n}_{i}\right)-\sqrtgm_{\imh}\,\hat{\bF}\left(\ol{\bU}^{n}_{i},\ol{\bU}^{n}_{i-1}\right)\right],
\end{equation}
\begin{equation}
    \ol{\bH}_{2}\equiv\ol{\bU}^{n}_{i}+\f{\Delta t_{i}}{1-\ve}\,\ol{\bQ}^{n}_{i},
\end{equation}
and
\begin{equation}
    \eta_{i}\equiv\f{\Delta t_{i}}{\ve\,\Delta V_{i}}.
\end{equation}

We proceed by focusing on each term individually, starting with the numerical flux term, $\ol{\bH}_{1}$.

\subsubsection{Numerical flux term}
We have to show that $\ol{\bH}_{1}\in\cG$. We again we use the Local-Lax-Friedrichs flux, \eqref{Eq:LLF}, yielding for $\ol{\bH}_{1}$:
\begin{align}
    \ol{\bU}^{n}_{i}-\f{\eta_{i}}{2}\Big\{&\sqrtgm_{\iph}\left[\bF\left(\ol{\bU}^{n}_{i+1}\right)+\bF\left(\ol{\bU}^{n}_{i}\right)-\alpha_{\iph}\left(\ol{\bU}^{n}_{i+1}-\ol{\bU}^{n}_{i}\right)\right]\\
    &-\sqrtgm_{\imh}\left[\bF\left(\ol{\bU}^{n}_{i}\right)+\bF\left(\ol{\bU}^{n}_{i-1}\right)-\alpha_{\imh}\left(\ol{\bU}^{n}_{i}-\ol{\bU}^{n}_{i-1}\right)\right]\Big\}\\
    &\hspace{-10em}=\left(1-\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}-\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\right)\ol{\bU}^{n}_{i}\\
    &\hspace{-8em}-\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\bF\left(\ol{\bU}^{n}_{i}\right)+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\bF\left(\ol{\bU}^{n}_{i}\right)\\
    &\hspace{-8em}+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\left[\ol{\bU}^{n}_{i-1}+\f{1}{\alpha_{\imh}}\bF\left(\ol{\bU}^{n}_{i-1}\right)\right]+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\left[\ol{\bU}^{n}_{i+1}-\f{1}{\alpha_{\iph}}\bF\left(\ol{\bU}^{n}_{i+1}\right)\right].
\end{align}
Now we add and subtract $\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\,\ol{\bU}^{n}_{i}$ and $\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\,\ol{\bU}^{n}_{i}$, yielding:
\begin{align}
    &\left(1-\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}-\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\right)\ol{\bU}^{n}_{i}\\
    &+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\left[\ol{\bU}^{n}_{i}-\f{1}{\alpha_{\iph}}\bF\left(\ol{\bU}^{n}_{i}\right)\right]+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\left[\ol{\bU}^{n}_{i}+\f{1}{\alpha_{\imh}}\bF\left(\ol{\bU}^{n}_{i}\right)\right]\\
    &+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\left[\ol{\bU}^{n}_{i-1}+\f{1}{\alpha_{\imh}}\bF\left(\ol{\bU}^{n}_{i-1}\right)\right]+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\left[\ol{\bU}^{n}_{i+1}-\f{1}{\alpha_{\iph}}\bF\left(\ol{\bU}^{n}_{i+1}\right)\right].
\end{align}
All of the terms in square brackets are similar to the $\ol{\bH}$ quantities in \citet{Qin2016}, and are therefore in $\cG$. It can easily be seen that the sum of the coefficients is unity. The final condition is that the coefficient of $\ol{\bU}^{n}_{i}>0$, or (recalling that $\eta_{i}=\Delta t_{i}/\left(\ve\,\Delta V_{i}\right)$):
\begin{align}
    1&-\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}-\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}>0\implies\eta_{i}\left(\sqrtgm_{\iph}\,\alpha_{\iph}+\sqrtgm_{\imh}\,\alpha_{\imh}\right)<1\\
    &\implies\Delta t_{i}<\f{\ve\,\Delta V_{i}}{\sqrtgm_{\iph}\,\alpha_{\iph}+\sqrtgm_{\imh}\,\alpha_{\imh}}\leq\f{\ve\,\Delta V_{i}}{2\,\text{max}\left(\sqrtgm_{i\pm\f{1}{2}}\,\alpha_{i\pm\f{1}{2}}\right)}.
\end{align}
Again we want a time-step that is the same for all elements at a given time, so:
\begin{equation}
    \Delta t<\text{min}_{i}\left(\f{\ve\,\Delta V_{i}}{2\,\text{max}\left(\sqrtgm_{i\pm\f{1}{2}}\,\alpha_{i\pm\f{1}{2}}\right)}\right).
\end{equation}

@@

\subsubsection{Source term}
For this section we drop the subscript $i$ and the superscript $n$. We have to show that $\ol{\bH}_{2}\in\cG$, where
\begin{equation}
    \ol{\bH}_{2}=\begin{pmatrix}\ol{D}\\ \ol{S}_{1}+\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\pd{\gamma_{kk}}{1}} \\ \ol{\tau}\end{pmatrix},\hspace{1em}\left(\ol{H}_{2}\right)_{1}>0,\hspace{1em}\left(\ol{H}_{2}\right)_{3}+\left(\ol{H}_{2}\right)_{1}>\sqrt{\left(\ol{H}_{2}\right)_{1}\left(\ol{H}_{2}\right)_{1}+\left(\ol{H}_{2}\right)_{2}\left(\ol{H}_{2}\right)^{2}}.
\end{equation}

It is clear that the first requirement for $\ol{\bH}_{2}$ is met, i.e. $\ol{D}>0$. The second requirement is:
\begin{align}
    \ol{D}+\ol{\tau}&>\sqrt{\ol{D}^{2}+\left[\ol{S}_{1}+\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}\right] \left[\ol{S}^{1}+\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\p^{1}\,\gamma_{kk}}\right] }\\
    &=\sqrt{\ol{D}^{2}+\left[\ol{S}_{1}+\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}\right] \left[\ol{S}^{1}+\gamma^{11}\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}\right] }\\
    &=\sqrt{\ol{D}^{2}+\ol{S}_{1}\,\ol{S}^{1}+\gamma^{11}\left[\f{\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}}{2\left(1-\ve\right)}\right]^{2}\left(\Delta t\right)^{2}+\f{\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}}{2\left(1-\ve\right)}\left[\ol{S}_{1}\,\gamma^{11}+\ol{S}^{1}\right]\Delta t}\\
    &=\sqrt{a\left(\Delta t\right)^{2}+b\,\Delta t+c}\geq0,
\end{align}
where
\begin{align}
    a&=\left[\f{\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}}{2\,\sqrt{\ol{\gamma_{11}}}\left(1-\ve\right)}\right]^{2}\geq0\\
    b&=\f{\ol{P^{kk}\,\pd{\gamma_{kk}}{1}}}{\ol{\gamma_{11}}\left(1-\ve\right)}\ol{S}_{1}=\f{2\,\ol{S}_{1}}{\sqrt{\ol{\gamma_{11}}}}\sqrt{a}\\
    c&=\ol{D}^{2}+\ol{S}_{1}\,\ol{S}^{1}\geq0.
\end{align}
The condition for a quadratic function to be positive-definite is that $a>0$ (concave-up) and $b^{2}-4\,a\,c<0$ (no real roots). The first condition is clearly met. For the second condition:
\begin{equation}
    b^{2}-4\,a\,c=\f{4\left(\ol{S}_{1}\right)^{2}}{\ol{\gamma_{11}}}a-4\,a\left(\ol{D}^{2}+\ol{S}_{1}\,\ol{S}^{1}\right)=4\,\ol{S}_{1}\,\ol{S}^{1}\,a-4\,a\ol{D}^{2}-4\,a\,\ol{S}_{1}\,\ol{S}^{1}=-4\,a\,\ol{D}^{2}<0.
\end{equation}
So, the square root is always positive.
